\documentclass[a4paper,10pt]{article}
\usepackage{anysize}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=0.6in, right=0.6in, top=0.25in, bottom=0.75in, includefoot, headheight=13.6pt]{geometry}
\usepackage{color,graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat's bookmarks
    pdftoolbar=true,        % show Acrobat's toolbar?
    pdfmenubar=true,        % show Acrobat's menu?
    pdffitwindow=true,      % page fit to window when opened
    pdftitle={Resume},    % title
    pdfauthor={MANU T S},     % author
    pdfsubject={Resume for placements},   % subject of the document
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=magenta,        % color of internal links
    citecolor=blue,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\definecolor{titleColor}{rgb}{0.85, 0.85, 0.85}

\begin{document}
{\qquad \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\}

%%%%%%%%%%___AREAS OF INTEREST____%%%%%%%%
  \colorbox{titleColor}{\parbox{6.5in}{\textbf{AREAS OF INTEREST}}}

    \begin{tabular}{p{2in}p{2in}p{2in}}
      $\circ$ Communication Systems	&$\circ$ Digital Signal Processing	&$\circ$ Error Correcting Codes \\
      $\circ$ Information Theory	&$\circ$ Wireless Communication 	&$\circ$ Software Defined Radio \\
    \end{tabular}

%%%%%%%%%%___TECHNICAL SKILLS____%%%%%%%%
  \colorbox{titleColor}{\parbox{6.5in}{\textbf{TECHNICAL SKILLS}}}
  
    \begin{itemize}
      \setlength{\itemsep}{1pt}
      \item \textbf{{Softwares Skills:}} GNU Radio, Scipy, Scilab and \LaTeX
      \item \textbf{{Programming Skills:}} C, C++, Python
      \item \textbf{{Software Defined Radio Platforms:}} USRP, RTL SDR
    \end{itemize}

%%%%%%%%%%% ____PROJECTS AND SEMINARS___ %%%%%%%%%%%
  \colorbox{titleColor}{\parbox{6.5in}{\textbf{PROJECTS AND SEMINARS}}}

    \begin{itemize}
    \setlength{\itemsep}{1pt}
    \item \textbf{M.Tech. Project:} \textbf{Application of LDPC codes to Multiuser Communications} \textbf \emph{(July 2013-Present)} \\
    {\textbf{Guide} - Prof. Sibiraj B Pillai, IIT Bombay.}

      We study LDPC encoding and decoding algorithms and extend them to multiuser scenario.
      Blocks for belief-propagation decoder and back-substitution encoder are designed.

    \item \textbf{Google Summer of Code, 2013:} \textbf{LDPC codes and more FEC in GNU Radio}  \textbf \emph{(June 2013-Present)}\\
    {\textbf{Mentor} - Dr.-Ing. Jens Elsner, CEL, KIT.} \\
      In this project we develop generic encoders and decoders for LDPC Codes in GNU Radio.
      
    \item \textbf{DARPA Spectrum Challenge:}\textbf \emph{(March 2013-Present)} \\
      During the hurdles and wild-card tournaments we designed a transmitter receiver pair using USRP and GNU Radio competing or cooperating with other pairs.
        
    \item \textbf{M.Tech. Seminar:} \textbf{Resource allocation in Wireless Networks}  \textbf \emph{(Nov. 2011)}\\
    {\textbf{Guide} - Prof. Sibiraj B Pillai, IIT Bombay.   }

       We studied optimal power allocation in a flat-fading multiple access channel in an Information Theoretic setup

    \item \textbf{Industrial Training:} \textbf{BSNL Kerala Circle}  \textbf \emph{(May 2008 - June 2008)}

      Various aspects of GSM Architecture were studied. Specifically, training on OMC Radio, OMC Switch, Radio Planning and BSS were 
      obtained

    \end{itemize}

% %%%%%%%%%%___COURSE WORKS___%%%%%%%%%%%
 \colorbox{titleColor}{\parbox{6.5in}{\textbf{COURSE WORK}}}
 
 \begin{tabular}{p{3.5in}p{5in}p{3.5in}}
    $\circ$ Communication Systems		&$\circ$ Error Correcting Codes \\
    $\circ$ Information Theory			&$\circ$ Digital Message Transmission \\
    $\circ$ Digital Signal Processing		&$\circ$ Wireless Communication \\
    $\circ$ Statistical Signal Analysis	&$\circ$ Applications of Linear Algebra \\
    $\circ$ Markov chains and Queuing Systems	&$\circ$ Optimization Techniques \\
\end{tabular}

%%%%%%%%%%___ACHIEVEMENTS____%%%%%%%%
 \colorbox{titleColor}{\parbox{6.5in}{\textbf{ACHIEVEMENTS}}}

 \begin{itemize}
 \item Our team secured a spot in the finals of \textbf{DARPA Spectrum Challenge}.
 \item Our team won first prize in Junk-Yard wars in Technozion 2010.
 \item \textbf{Best outgoing student} of the year 2004 in JNV Malampuzha.
  \end{itemize}

%%%%%%%%%%% ____WORK EXPERIENCE___ %%%%%%%%%%%
  \colorbox{titleColor}{\parbox{6.5in}{\textbf{WORK EXPERIENCE}}}

    \begin{itemize}
      \setlength{\itemsep}{1pt}
      \item \textbf{Graduate Engineering Trainee ( C \& I ), Adani Power Limited}  \textbf \emph{(July 2010-January 2011)}
      \item \textbf{Senior Engineer ( C \& I ), Adani Power Limited}  \textbf \emph{(January 2011-July 2011)}
    \end{itemize}
    
%%%%%%%%%%___HOBBY___%%%%%%%%%%%
\colorbox{titleColor}{\parbox{6.5in}{\textbf{HOBBIES}}}

\begin{itemize}
 \setlength{\itemsep}{1pt}
    \item Reading, coding, music and movies.
  \end{itemize}

\end{document}
